Echoes from the scattering of wavepackets on wormholes

### 2019-01-16 paper.tex
Add files via upload

The dispersion of scalar waves by a Schwarzschild black hole has been thoroughly studied \citep{doi:10.1063/1.522949, Sanchez:1976xm, Sanchez:1977si, Sanchez:1977vz}, it is crucial for our purposes to provide the full solution since it contains all the information of the potential barriers constituting the effective potential in the case of a wormhole. The dynamics of the scattering problem is found by solving the equation of motion for a test scalar field

@@

\left[-\partial_t^2+\partial_x^2-V_{\mathrm{scalar}}(x)\right]\mathcal{U}^{\mathrm{bh}}_{\ell m}(x,t) = 0,

@@

and the effective potential $V_{\mathrm{scalar}}(x)$ is given by

@@

V_{\mathrm{scalar}}(x) = \left(1-\frac{r_g}{r(x)}\right)\left[\frac{\ell(\ell+1)}{r(x)^2}+\frac{r_g}{r(x)^3}\right].

>>>>

Our primary objective is to study the dynamics of scalar and tensor wavepackets scattering a Misner-Thorne wormhole at all points. Thus, we first review the dispersion of scalar waves by a Schwarzschild black hole, thoroughly studied in \citep{doi:10.1063/1.522949, Sanchez:1976xm, Sanchez:1977si, Sanchez:1977vz}, wherein the collision against each of the two potential walls (constituting the effective potential cavity formed by a wormhole) is studied in full detail. The dynamics of the scattering problem is found by solving the equation of motion for a test scalar field

@@

\left[-\partial_t^2+\partial_x^2-V^{\mathrm{bh}}_{\mathrm{scalar}}(x)\right]\mathcal{U}^{\mathrm{bh}}_{\ell m}(x,t) = 0,

@@

and the effective potential $V^{\mathrm{bh}}_{\mathrm{scalar}}(x)$ is given by

@@

V^{\mathrm{bh}}_{\mathrm{scalar}}(x) = \left(1-\frac{r_g}{r(x)}\right)\left[\frac{\ell(\ell+1)}{r(x)^2}+\frac{r_g}{r(x)^3}\right].
